% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}
 
\name{Dana Atchley Merrick}
\address{\,\,\, dana.merrick@gmail.com}
\address{Acton, MA -- 978.206.1331}
 
\begin{resume}

\section{HIGHLIGHTS}
	\begin{itemize}  \itemsep -2pt % reduce space between items
		\item Detail oriented, fast learner.
		\item Motivated problem solver.
		\item Good communication skills.
		\item Works well with others.
	\end{itemize}

\section{EXPERIENCE}
	{\sl Web Software Developer} \hfill Summer 2009 \\
	Wieck Media, 
	Dallas, TX
	\begin{itemize}  \itemsep -2pt % reduce space between items
		\item Pure Ruby development; contributing to the company's in-house web framework (and Rails alternative), called ``Harbor."
		\item Designed and developed libraries (gems) for user, media, and release management, including a heavy focus on i18n for an international client.
	\end{itemize}
 
	{\sl System Administrator} \hfill            Summers/Holidays 2006-2009 \\
	Integrated Computer Solutions,
	Bedford, MA
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Managed the server infrastructure for all of the in-house machines, including production servers, personal work stations, virtual machines, and legacy hardware.
		\item Built server monitoring system, cared for physical servers, maintained software.
		\item Contributed to the newest version of their sister company's project management suite, called ``Project.net."
		\item Helped a team of UI designers create tools to manage offshore workers and a full-featured online timecard system.
	\end{itemize} 

\section{EDUCATION}
	{\sl Trinity College,}
	Hartford, CT \hfill May 2010 \\
	Bachelor of Science, Double Major \\
	Computer Science \& Classical Mathematics \\
	Cumulative GPA: 3.0/4.0 \\
	Founding member: Hartford Ruby Brigade \\
	\\
	{\sl Kimball Union Academy,}
	Meriden, NH \hfill May 2006 \\
	Cum Laude \\
	Cumulative GPA: 3.9/4.0 \\
	\\
	{\sl Minuteman Regional High School,}
	Lexington, MA \hfill 2001-2004 \\
	Bronze medal in national robotics competition (SkillsUSA VICA 2003)
	
\section{RELATED COURSES}
	{\sl Computer Science:}
	Advanced Web Programming,
	Database Fundamentals,
	Theory of Computation,
	Data Structures \& Algorithms,
	Systems Software.
	\\
	{\sl Mathematics:}
	Graph Theory,
	Combinatorics and Computing.
                
\section{COMPUTER \\ SKILLS}
	{\sl Fluent:} 
	Ruby, 
	Java, 
	SQL, 
	PHP, 
	JavaScript, 
	HTML, 
	bash,
	sed.
	\\
	{\sl Advanced:}
	C/C++, 
	git,
	Scheme,
	Haskell,
	\LaTeX,
	Perl.
	\\
	{\sl Proficient:} 
	Clojure,
	Qt,
	AWK,
	Common Lisp.
	\\
	{\sl Operating Systems:}
	GNU/Linux, OS X, UNIX/BSD, ESX.
	\\
	{\sl Expertise:}
	UI design,
	networking,
	regular expressions,
	security.

\section{LOOKING FOR}
	Opportunity to be rewarded for innovation and leadership. \\
	Camaraderie with an intelligent team. \\
	Adoption of modern technologies.
	
%\section{REFERENCES}
%  	Available upon request.
	
\end{resume}
\end{document}







