\documentclass[12pt]{amsart}

\textwidth=1.25\textwidth
\calclayout


\begin{document}

\thispagestyle{empty}

\begin{center}
{\bf Math 331  --- Homework 4 \\
Due:  Friday, February 26}
\end{center}

\bigskip

\noindent
Dana Merrick \\
\today

\bigskip

\begin{enumerate}

\setlength{\itemsep}{6pt}

\item Prove that for any natural number $N$, if $\{ I_1,I_2,\ldots,I_N\}$
  is a finite collection of of closed intervals, then the set
%
\[ E = \bigcup_{n=1}^N I_n \]
%
is compact:  i.e., every open cover of $E$ has a finite subcover.

Hint:  use induction, the Heine-Borel theorem, and the proof of the
Heine-Borel theorem.

\begin{proof}
First we will show that every $I_n$ is both closed and bounded. Each $I_n$ is closed by their definition, and bounded by the fact that they are closed.

%Let U be the set of all of the upper bounds of the $I_n$s, and L be the set containing all of the lower bounds of the $I_n$s. Then $\sup U$ is an upper bound for the set of $I_n$s, and $\inf L$ is a lower bound for the set of $I_n$s.

We will proceed by induction on $N$. As a base case, if $N=2$, then we're working with the set $I_1\cup I_2$. Let $O$ be an open cover of this set. Then $O$ must cover both $I_1$ and $I_2$. Since every $I_n$ is closed and bounded, by the Heine-Borel theorem both $I_1$ and $I_2$ are compact, there must be a finite subcover of each. Let $S_1$ be the finite subcover of $I_1$, and $S_2$ be the finite subcover of $I_2$. Then $S_1\cup S_2$ is finite and covers $I_1\cup I_2$.

Assume that the set
\[ A = \bigcup_{n=1}^k I_n \]
is compact for some integer $k$. In other words, every open cover of $A$ has a finite subcover. We want to show that every open cover of the set
\[ B = \bigcup_{n=1}^{k+1} I_n = A \cup I_{k+1} \]
also has a finite subcover.

Let $O_B$ be an open cover of $B$. Then $O_B$ must cover both $A$ and $I_{k+1}$. By our inductive hypothesis, every open cover of the set $A$ contains a finite subcover. Since $I_{k+1}$ is both closed and bounded, by the Heine-Borel theorem every open cover of it contains a finite subcover. Let $S$ be the union of the finite subcover of the cover $O_B$ for the sets $A$ and $I_{k+1}$. Since both subcovers are finite and cover $A \cup I_{k+1}$, then the set $B$ must be compact.

\end{proof}

\item Construct a counter-example to show that previous result is not true if $E$ is the union
  of a countable set of closed intervals $\{I_n : n \in \mathbb N \}$.  

\begin{proof}
Define $I_n$ as $[-n,n]$. Then each $I_n$ is closed but
\[ E = \bigcup_{n\in\mathbb N} I_n \]
is unbounded. Hence, by the Heine-Borel theorem, $E$ is not compact.
\end{proof}

\end{enumerate}


\end{document}
